Visualizations for the manuscript

### 2022-10-18 metanalysis_visualization/manuscript_Figures.Rmd
fixing subgroup disorders join bug

```{r, include=FALSE}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, time, sex ) %>%
  summarise( total = sum( count ), 
             count_sex = sum( count_sex ), 
             percentage = 100* count_sex / total, 
             siteid = "ALL") %>%  
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  mutate(month_year = format(time_p, "%m")) %>% 
  select(time_p, time, period, sex, count_sex, percentage, siteid, month_year)
```

@@

perc_disorder_group_complete <- perc_disorder_group_all %>% 
  full_join(table_iterations_disorder) %>% 
  arrange(siteid, time_p, disorder_group) %>% 
  group_by(siteid, time_p) %>% 
  fill(count_icd, 
       period, 
       country , 
       plotsLabel, 
       .direction = "downup") %>% 
  ungroup() %>% 
  replace_na(list(count_dg = 0, percentage_dg = 0))

@@

```{r}
observed_coefficients_df_disorder <- perc_disorder_group_total %>% 
  group_by(disorder_group) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation, 
               slope_name = c("time", "periodduring_pandemic:time")
               ) %>% 
  rename(observed_slope_coefficient = estimate) %>% 
  pivot_wider(names_from = term,
              values_from = observed_slope_coefficient) %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`) %>% 
  mutate(during_slope = before_slope + difference_slope) %>% 
  pivot_longer(cols = c(before_slope, difference_slope, during_slope), 
               names_to = "term", 
               values_to = "observed_slope_coefficient")

@@

bootstrapped_disorders <- perc_disorder_group_total %>%
  group_by(disorder_group) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_map( ~bootstrapping_slopes(.x,
                                   group_name = .y,
                                   bootstrap_size = bootstrap_size,
                                   count = "dg_cases", 
                                   percentage = "percentage"))
names(bootstrapped_disorders) <- unique(perc_disorder_group_total$disorder_group)

@@

```{r, fig.height=15, fig.width=25}
bootstrapped_fitted_disorder %>% 
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(x = time + 0.5, color = period), alpha = 0.03) +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = interaction(quantiles, period)),
            data = filter(quantile_bootstrapped_fitted_disorder, quantiles %in% c("2.5%", "97.5%")),
            linetype = "dashed") +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = period),
            data = filter(quantile_bootstrapped_fitted_disorder, quantiles == "50%")) +
  geom_point(aes(x = time + 0.5, y = percentage, group = NULL),
             data = filter(perc_disorder_group_total, disorder_group %in% disorders_to_select),
             alpha = 0.5) +
  scale_x_continuous(breaks = breaks_width(1),
                     labels = time_to_time_p, 
                     limits = c(2, 29),
                     expand = c(0.03,0)) + 
  geom_vline(xintercept = 16, linetype = 6 ) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    # subtitle = "Parametric bootstrap estimation: (10000 iterations)",
    x = "Calendar dates",
    y = "Percentage",
    color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom")

@@

counts <- patient_count_psy_period_psy_all %>%
  select( plotsLabel, time_p, time, month_year, count_psy_patients, total_cases = count_icd )

counts2 <- reshape2::melt(counts ,  id.vars = c('plotsLabel', 'time_p', 'time','month_year'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "Patients with mental health disorder", counts2$group )
counts2$group <- gsub("total_cases", "Total number of patients", counts2$group )

@@

#### All together
```{r}
counts_agg <- counts %>%
  group_by( time_p ) %>%
  mutate( psy_cases = sum( count_psy_patients), 
    total_cases = sum(total_cases)) %>%
  select( time_p, time, month_year, psy_cases, total_cases)

counts_agg2 <- reshape2::melt(counts_agg ,  id.vars = c('time_p', 'time','month_year'), variable.name = 'group')
counts_agg2$group <- gsub("count_psy_patients", "Patients with mental health disorder", counts_agg2$group )
counts_agg2$group <- gsub("total_cases", "Total number of patients", counts_agg2$group )

>>>>

```{r, include=FALSE}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, time, sex ) %>%
  summarise( total = sum( count ), 
             count_sex = sum( count_sex ), 
             percentage = 100* count_sex / total, 
             siteid = "ALL") %>%  
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, time, period, sex, count_sex, percentage, siteid)
```

@@

perc_disorder_group_complete <- perc_disorder_group_all %>% 
  full_join(table_iterations_disorder) %>% 
  arrange(siteid, time_p, disorder_group) %>% 
  group_by(siteid, time_p) %>% # grouping by time prevent following function from wokring as expected
  fill(count_icd, 
       period, 
       country , 
       plotsLabel, 
       .direction = "downup") %>% 
  ungroup() %>% 
  replace_na(list(count_dg = 0, percentage_dg = 0)) %>% 
  select(-time) %>% 
  # Readfing consistent time information 
  left_join(time_timep_df, by = "time_p")

@@

```{r}
observed_coefficients_df_disorder <- perc_disorder_group_total %>% 
  group_by(disorder_group) %>% 
  group_modify(coefficient_slope_calculation, 
               slope_name = c("time", "periodduring_pandemic:time")
               ) %>% 
  rename(observed_slope_coefficient = estimate) %>% 
  pivot_wider(names_from = term,
              values_from = observed_slope_coefficient) %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`) %>% 
  mutate(during_slope = before_slope + difference_slope) %>% 
  pivot_longer(cols = c(before_slope, difference_slope, during_slope), 
               names_to = "term", 
               values_to = "observed_slope_coefficient")

@@

bootstrapped_disorders <- perc_disorder_group_total %>%
  group_by(disorder_group) %>% 
  group_map( ~bootstrapping_slopes(.x,
                                   group_name = .y,
                                   bootstrap_size = bootstrap_size,
                                   count = "dg_cases", 
                                   percentage = "percentage"))
names(bootstrapped_disorders) <- unique(perc_disorder_group_total$disorder_group)

@@

```{r, fig.height=15, fig.width=25}
bootstrapped_fitted_disorder %>% 
  # mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(x = time + 0.5, color = period), alpha = 0.03) +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = interaction(quantiles, period)),
            data = filter(quantile_bootstrapped_fitted_disorder, quantiles %in% c("2.5%", "97.5%")),
            linetype = "dashed") +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = period),
            data = filter(quantile_bootstrapped_fitted_disorder, quantiles == "50%")) +
  geom_point(aes(x = time + 0.5, y = percentage, group = NULL),
             data = filter(perc_disorder_group_total, disorder_group %in% disorders_to_select),
             alpha = 0.5) +
  scale_x_continuous(breaks = breaks_width(1),
                     labels = time_to_time_p, 
                     limits = c(2, 29),
                     expand = c(0.03,0)) + 
  geom_vline(xintercept = 16, linetype = 6 ) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    # subtitle = "Parametric bootstrap estimation: (10000 iterations)",
    x = "Calendar dates",
    y = "Percentage",
    color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom")

@@

counts <- patient_count_psy_period_psy_all %>%
  select( plotsLabel, time_p, time, count_psy_patients, total_cases = count_icd )

counts2 <- reshape2::melt(counts ,  id.vars = c('plotsLabel', 'time_p', 'time'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "Patients with mental health disorder", counts2$group )
counts2$group <- gsub("total_cases", "Total number of patients", counts2$group )

@@

#### All together
```{r}
counts_agg <- counts %>%
  group_by( time_p ) %>%
  mutate( psy_cases = sum( count_psy_patients), 
    total_cases = sum(total_cases)) %>%
  select( time_p, time, psy_cases, total_cases)

counts_agg2 <- reshape2::melt(counts_agg ,  id.vars = c('time_p', 'time'), variable.name = 'group')
counts_agg2$group <- gsub("count_psy_patients", "Patients with mental health disorder", counts_agg2$group )
counts_agg2$group <- gsub("total_cases", "Total number of patients", counts_agg2$group )
